% !TEX program = xelatex
\documentclass[letterpaper,11pt]{article}
\usepackage[hmargin=.75in,vmargin=.3in]{geometry}
\linespread{1}% Single line space
\pagestyle{empty}% Suppress page numbers
\usepackage[parfill]{parskip}% Remove paragraph indentation
% English font
\usepackage{fontspec}
\setmainfont{Times New Roman}
%
% Narrow vertical space of itemize
\usepackage{enumitem}
\setlist{itemsep=0pt,partopsep=0pt,parsep=0pt,topsep=0ex}
%
\usepackage{hyperref} % Hyperlink
\begin{document}
\begin{center}
    {\LARGE\bfseries{}Jialin CHEN}\\
    \vspace{1ex}
    96 JinZhai Rd., Hefei, Anhui, 230026, P.R.China\\
    chenjialin@mail.ustc.edu.cn | chenjl@shanghaitech.edu.cn | +86 158-5868-9289\\
    \href{https://github.com/Chen-Jialin}{github.com/Chen-Jialin}\\
\end{center}
\vspace{-1ex}

{\Large\bfseries{}EDUCATION}\\
\vspace{-1ex}
\rule[1.5ex]{\columnwidth}{1pt}
{\large\bfseries\scshape{}ShanghaiTech University}, {Shanghai, China}\hfill{Sep. 2017 -- Jul. 2021}\\
{\itshape{}Bachelor of Science, Physics}\\
\vspace{-4ex}
\begin{itemize}
    \item GPA: \textbf{3.88/4.0} | Rank in major: 1/38 | Rank in SPST (School of Physical Science and Technology): 1/91
    \item Merit Scholarship (Academic Top: 12\%; 2017\textasciitilde2018, 2018\textasciitilde2019 \& 2019\textasciitilde2020), Outstanding Graduate
    \item Relevant courses: Laser Principles and Technologies, Femtosecond Laser and Ultrafast Spectroscopy, Nonlinear Optics, Communication System, Guided Wave Optics
\end{itemize}
{\large\bfseries\scshape{}University of Science and Technology of China}, {Anhui, China}\hfill{Sep. 2021 -- Present}\\
{\itshape{}Master of Engineering, Optical Engineering}\\
\vspace{-2ex}% \vspace{1ex}

{\Large\bfseries{}RESEARCH EXPERIENCE}\\
\rule[1.5ex]{\columnwidth}{1pt}
\vspace{-4ex}\\
{\large\bfseries\scshape{}ShanghaiTech University}, Shanghai, China\hfill{2017 -- 2021}\\
{\bfseries\itshape{}Undergraduate Researcher, Ultrafast and Nonlinear Optics Group | PI: John A. McGuire}\hfill{\itshape{}Jun. 2020 -- Jul. 2021}\\
\vspace{-4ex}
\begin{itemize}
    \item Learning 2D electric spectroscopy (2D-ES) experiment technology.
    \item Collaborating in building a 2D-ES system, programming with LabVIEW for line-scan CMOS sensor controlling and optimizing data processing modules, reducing the run time of some modules by more than 50\%.
\end{itemize}
\vspace{-1ex}
{\bfseries\itshape\fontdimen2\font=0.1em{}Undergraduate Researcher, Scanning Tunneling Microscope (STM) Group | PI: Shichao Yan}\hfill{\itshape{}Jul. 2018 -- May 2020}\\
\vspace{-4ex}
\begin{itemize}
    % \item Learned scanning tunneling microscope experiment technology.
    \item Designed two holders of STM tip etching devices with SolidWorks to improve safety and efficiency of tip etching process.
    \item Drew a 3D model for the whole lab and its internal facilities for the convenience of the arrangement of the equipments in the lab.
\end{itemize}
% \vspace{1ex}

{\Large\bfseries{}COMPETITIONS AND AWARDS}\\
\rule[1.5ex]{\columnwidth}{1pt}\\
\vspace{-5ex}
\begin{itemize}
    \item {\bfseries{}Interdisciplinary Contest In Modeling (ICM)}, {Honorable Mention}\hfill{Feb. 2020}
    \item {\bfseries{}Chinese Undergraduate Mathematical Contest in Modeling}, {Second Prize in Shanghai}\hfill{Dec. 2019}
    \item {\bfseries{}China Undergraduate Physics Tournament (CUPT)}: Collaborated with another partner to complete 4 research sub-projects, delivered 5 public presentations and won 3 awards in total:
    \begin{itemize}
        \item[$\circ$] {National Second Prize}\hfill{\itshape{}Aug. 2019}
        \item[$\circ$] {Second Prize in Shanghai}\hfill{\itshape{}Jul. 2019}
        \item[$\circ$] {Second Prize in East China}\hfill{\itshape{}May 2019}
    \end{itemize}
\end{itemize}
% \vspace{1ex}

{\Large\bfseries{}WORKING EXPERIENCE}\\
\rule[1.5ex]{\columnwidth}{1pt}
\vspace{-4ex}\\
{\large\bfseries\scshape{}ShanghaiTech University}, Shanghai China\hfill{2017 -- 2021}\\
{\bfseries\itshape{}Quantum~~Physics~~Lab~~in~~Atomic~~Physics}, {\itshape{}Teaching Assistant}\hfill{\itshape{}Mar. 2021 -- Jun. 2021}\\
\vspace{-4ex}
\begin{itemize}
    \item Guided the students with experiments and reviewed their presentation and essays.
\end{itemize}
\vspace{-1ex}
{\bfseries\itshape{}Innovative~~Laboratory~~for~~Physics~~Tournament}, {\itshape{}Teaching Assistant}\hfill{\itshape{}Jul. 2020 -- Aug. 2020}\\
\vspace{-4ex}
\begin{itemize}
    \item Assisted the instructor with lectures and office hour.
\end{itemize}
\vspace{-1ex}
% {\bfseries\itshape{}Center~~for~~Innovative~~Teaching~~and~~Learning}, {\itshape{}Administrative Assistant}\hfill{\itshape{}May 2020 -- Jan. 2021}\\
% \vspace{-4ex}
% \begin{itemize}
%     \item Responsible for secretarial work concerned with undergraduate educational administration, including material collection, survey form design and document translation.
%     \item Prepared meeting materials, received and registered the participants in teaching seminars and workshops.
% \end{itemize}
% \vspace{-1ex}
{\bfseries\itshape{}Principle~~of~~Physics~~I~~Laboratory}, {\itshape{}Teaching Assistant}\hfill{\itshape{}Sep. 2019 -- Jan. 2020}\\
\vspace{-4ex}
\begin{itemize}
    \item Trained first-year undergraduates in physics with some commonly-used software (including MATLAB, Adobe Illustrator, Excel, and Tracker), and the usage of high-speed camera.
    % \item Prepared the experiment equipments before classes.
    \item Guided the students with experiments and reviewed their reports.
    \item Assisted the instructors to guide the students with two exploratory experiment projects.
\end{itemize}
% \vspace{1ex}

{\Large\bfseries{}SKILLS AND OTHERS}\\
\rule[1.5ex]{\columnwidth}{1pt}\\
\vspace{-5ex}
\begin{itemize}
    \item Languages: Chinese (Native); English (Fluent), TOEFL: 100
    \item Software \& Programming Languages: Python, MATLAB, LabVIEW, Fortran, \LaTeX, Adobe Illustrator, SolidWorks
    \item GRE: 328+3.5; GRE Subject (Physics): 970
    % \item Red Cross Basic First-aid Training Certificate
\end{itemize}
\end{document}